---
title: "Visualizations"
date: 02-24-2026
---

# Data Visualization for Brexit Data

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)

brexit_data <- read_csv("data/Brexit 5000 Sample Anonymized.csv")
colnames(brexit_data)

```

## Visualization 1: Tone Distribution

```{r echo=FALSE, message=FALSE, warning=FALSE}
summary(brexit_data$Commenter_BA_Score)

library(ggplot2)

ggplot(brexit_data, aes(x = Commenter_BA_Score, fill = Cross_Cutting_w_Counters)) +
  geom_density(alpha = 0.4) +
  labs(
    title = "Aggression Distribution by Cross-Cutting Expression",
    x = "Behavioral Aggression Score"
  ) +
  theme_minimal()
```

### Aggression Distribution

Aggression is not limited to cross-cutting exchanges. Like-minded comments appear highly concentrated at the upper end of the aggression scale, suggesting that emotional intensity may be amplified within ideologically aligned groups. Cross-cutting discussions show more variation, indicating that disagreement alone does not necessarily drive hostility.

## Visualization 2: Participant Concentration

```{r echo=FALSE, message=FALSE, warning=FALSE}

library(ineq)

counts <- brexit_data %>% count(Commenter_ID)
ineq(counts$n, type = "Gini")

brexit_data %>%
  count(Commenter_ID, sort = TRUE) %>%
  slice_head(n = 10) %>%
  ggplot(aes(x = reorder(Commenter_ID, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Top 10 Most Active Participants",
    x = "Participant ID",
    y = "Number of Comments"
  ) +
  theme_minimal()

```

### Top 10 Most Active Participants

Participation is highly unequal. A small number of users contribute a disproportionately large share of comments, while most participants are far less active. This suggests that online political discourse may be shaped primarily by a vocal minority rather than broad engagement.
